Creating the ``r params$package_name`` R package

### 2025-07-23 create-FSHybridPLS.Rmd
ridge type formulation
delete gram matrix testthat

```{r}
testthat::test_that("Gram matrix edge cases", {
  suppressPackageStartupMessages(library(fda))

  # Case 1: Fourier basis (orthogonal over [0, 1])
  fb <- create.fourier.basis(rangeval = c(0, 1), nbasis = 5)
  J_fourier <- compute_gram_matrix(fb)
  testthat::expect_equal(J_fourier, diag(diag(J_fourier)), tolerance = 1e-10)  # Nearly diagonal

  # Case 2: Constant basis (1 basis function)
  cb <- create.constant.basis(rangeval = c(0, 1))
  J_const <- compute_gram_matrix(cb)
  testthat::expect_equal(dim(J_const), c(1, 1))
  testthat::expect_equal(J_const[1, 1], 1)

  # Case 3: Invalid input
  testthat::expect_error(compute_gram_matrix("not a basisfd"))

  # Case 4: Highly localized B-splines
  # Simulate nearly disjoint support (narrow B-splines)
  narrow_bs <- create.bspline.basis(rangeval = c(0, 1), nbasis = 10, norder = 2)
  J_narrow <- compute_gram_matrix(narrow_bs)
  testthat::expect_true(all(abs(J_narrow[upper.tri(J_narrow)]) < 0.5))  # off-diagonals small
})

@@

    basis_i <- fd_i$basis
    gram_list[[i]] <- compute_gram_matrix(basis_i)
    n_basis_list[i] <- basis_i$nbasis
  }

  structure(
    list(
      Z = Z,
      functional_list = functional_list,
      gram_list = gram_list,
      n_basis_list = n_basis_list,
      n_sample = n_sample,
      n_functional = n_functional,
      n_scalar = n_scalar
    ),
    class = "predictor_hybrid"
  )
}
```

@@

compare xi_hat_lin, xi_hat_lin_new

>>>>

@@

    basis_i <- fd_i$basis
    gram_list[[i]] <- compute_gram_matrix(basis_i)
    gram_deriv2_list[[i]] <- compute_gram_matrix_deriv2(basis_i) # New function call

    n_basis_list[i] <- basis_i$nbasis
  }

  structure(
    list(
      Z = Z,
      functional_list = functional_list,
      gram_list = gram_list,
      gram_deriv2_list = gram_deriv2_list, # Store the new list
      n_basis_list = n_basis_list,
      n_sample = n_sample,
      n_functional = n_functional,
      n_scalar = n_scalar
    ),
    class = "predictor_hybrid"
  )
}
```

@@

### helper: get_xi_hat_linear
```{r}
get_xi_hat_linear_new <- function(W, y){
  # new
  ## step 1: inner products
  u <- list()
  u_j <- B %*% t(Theta_j) %*% y
  for (j in 1:K){
    Theta_t <- W$functional_list[[j]]$coefs
    B <- W$gram_list[[j]]
    u[[j]] <- B %*% Theta_t %*% y
  }
  v <- t(W$Z) %*% y

  ## step 2: squared norm
  q <- sum(v^2)
  for (j in 1:K){
    Theta_t <- W$functional_list[[j]]$coefs
    R <- W$gram_list[[j]]
    u[[j]] <- B %*% Theta_t %*% y
  }  
  # old
  n <- W$n_sample
  K <- W$n_functional
  normalizer <- 0

  for (i in 1:K){  ## tPhi_tC : C multiplied by Phi. Scalable to arbitrary K

    d[[i]] <- Theta_t %*% y
    normalizer <- normalizer + t(y) %*% t(Theta_t) %*% B %*% Theta_t %*% y
  }
  normalizer <- normalizer+ t(y) %*% W$Z %*% t(W$Z) %*% y
  d_vec <- do.call(c, d)  # or: unlist(d)
  d_vec <- d_vec/ sqrt(normalizer)
  return(d_vec)
}
```
